Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-20 manuscript.tex
first quickpass through sec 6

\noindent On-site construction will proceed in stages, starting from the
initial 37 elements that will be in place by project start.  These will be used
in conjunction with the thoroughly characterized extant PAPER signal path and
processing hardware for a very low risk initiation of scientific observations
from the very beginning.  Additionally, the 19 HERA elements currently in
place will also have had an extensive period of commissioning
and characterization.  As elements 38 to 128 are installed in year 1, they can
immediately be placed within the array and be used for observing.

During this period, infrastructure for the new node-based system is installed
and tested with the first elements beyond 128.  After the HERA-128 observing
season, the full array is transitioned to use HERA's new hardware infrastructure.  In this same time frame, the existing PAPER processing
container is moved to the edge of the array to house the timing sub-system
and fiber optic splice cabinet while the correlator will move to the KAPB.
Also, the data processing activity at Penn is transitioned to NRAO.
Summarizing, the hardware deployment phases are in four categories:
\begin{enumerate}
\item Element construction:  linear process (years 1, 2 \& 3)
\item Infrastructure:  (a) node power and fiber reticulation (years 1 \& 2), (b) container relocation (year 1), (c) node installation (years 2 \& 3)
\item Signal path:  convert to node-based system after 128 elements (years 2 \& 3)
\item Processing:  (a) data processor/server to NRAO (year 1), (b) X-engine \& real-time processor/storage to KAPB (year 2)
\end{enumerate}

@@

The optimal EoR observing window is from September to April, with power spectrum limit results appearing about one year later.  Concurrent technique development and deployment will be on-going. Additional information is in the project management plan.
\begin{itemize}[leftmargin=0.7in]
\item[Year 1:] Observe with H37.  Real-time data pipeline, delay-space power spectrum (DSPS) pipeline, FHD pipeline.  21\,cm framework for incorporating with other probes. Construct H128.
\item[Year 2:] Observe with H128.  Real-time calibration pipeline.  DSPS/FHD/global sky model integration. Snapshot imaging pipeline.  EoR parameter estimation development.  H37 results.  Construct H240.  {\em Data products:  power spectrum, Stokes I maps.}
\item[Year 3:] Observe with H240.  Foreground-filtered imaging pipeline.  EoR parameter estimation development.   H128 results. Construct H350.  {\em Data products:  power spectrum, Stokes IQUV maps, foreground image cube.}
\item[Year 4:] Observe with H350.  EoR parameter estimates.  H240 results.  {\em Data products:  power spectrum, global sky model IQUV, snapshots, foreground-filtered image cube.}
%\item[Year 5:] Observe with H350.  H350 results.  {\em Data products:  power spectrum, global sky model IQUV, snapshots, foreground-filtered image cube.}
\end{itemize}

>>>>

\noindent On-site construction will proceed in stages, starting from the
initial 19 element currently in place.    Elements 20-37
are currently under construction, to be completed in 2016.  
 These will be used
in conjunction with the thoroughly characterized extant PAPER signal path and
processing hardware for a very low risk initiation of scientific observations.
As elements 38 to 128 are installed in 2017, they can
immediately be placed within the array and be used for observing.

During this period, infrastructure for the new node-based system will be installed
and tested with the first elements beyond 128.  After the HERA-128 observing
season, the full array will be transitioned to use HERA's new hardware infrastructure.  
In this same time frame, the existing PAPER processing
container will be moved to the edge of the array to house the timing sub-system
and fiber optic splice cabinet while the correlator will move to the KAPB.
 The overall plan
is shown in Figure \ref{fig:timeline}.

@@

The optimal EoR observing window is from September to April, with power spectrum limit results appearing about one year later.  Concurrent technique development and deployment will be on-going.
\begin{itemize}[leftmargin=0.7in]
\item[2016/17:] Observe with H37.  Real-time data pipeline, delay-space power spectrum (DSPS) pipeline, FHD pipeline.  21\,cm framework for incorporating with other probes. Construct H128.
\item[2017/18:] Observe with H128.  Real-time calibration pipeline.  DSPS/FHD/global sky model integration. Snapshot imaging pipeline.  EoR parameter estimation development.  H37 results.  Construct H240.  {\em Data products:  power spectrum, Stokes I maps.}
\item[2018/19:] Observe with H240.  Foreground-filtered imaging pipeline.  EoR parameter estimation development.   H128 results. Construct H350.  {\em Data products:  power spectrum, Stokes IQUV maps, foreground image cube.}
\item[2019/20:] Observe with H350.  EOR parameter estimates.  H240 results.  {\em Data products:  power spectrum, global sky model IQUV, snapshots, foreground-filtered image cube.}
\item[2020+:] Observe with H350.  H350 results.  {\em Data products:  power spectrum, global sky model IQUV, snapshots, foreground-filtered image cube.}
\end{itemize}
